Compositional equivalences based on Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-04-30 2016-Weak-FH-Bisim/WeakBisim.tex
Huge pass on lemma 4

We use ${\displaystyle \bigotimes_{i=n}^{0} \Post_i}$ to denote  $\Post_n\otimes .. \otimes \Post_0$. By convention ${\displaystyle \bigotimes_{i=-1}^{0} \Post_i}$ is the identity.

@@

\begin{lemma}
\label{lem-rel-OT-WOT} Let $A = <J,\mathcal{S}, s_0,
    \mathcal{T}>$ be open automata and $<J,\mathcal{S}, s_0,
    \WT>$ be the
weak open automata derived from $A$.  The two following statements are equivalent
%For any weak open transition $\symb{WOT} \in \WT$, there exists an open transitions $\symb{OT} \in \mathcal{T}$ such that:\\
\begin{enumerate}
\item Either $   
\alpha = \tau \wedge  \set{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'$; or \\ 
there exist   $\set{\beta^1}_i$, $\set{\beta^2_i}$, and $\set{\beta^3_i}$, $\Pred^1_i$, $\Pred^3_i$, $\Post^1_i$, and  $\Pred^2$, $\Post^2$ s.t.:
\begin{mathpar}
%\mprset {vskip=.5ex}
%\inferrule 
\forall i \in [0..n].\openrule
    {
       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T} \quad \wedge
\quad
\openrule
         {
           \set{\beta^2},\Pred^2,\Post^2 }
         {s_0^2 \OTarrow {\alpha} s_1^2} \in \mathcal{T}
\quad \wedge\\
\forall i \in [0..m].\openrule
         {
           \set{\beta^3_i},\Pred^3_i,\Post_i^3    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
 \end{mathpar}
\item  there exist $\set{\gamma}$, $\Pred$, $\Post$ s.t.
 \begin{mathpar}
%   \Longleftrightarrow  {
\openrule
         {
           \set{\gamma},
		\Pred, \Post
				 } {s \OTWeakarrow {\alpha'} s'} \in\WT
%}
\end{mathpar}
\TODO{changer alpha...}\\
where\\
$
\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=n}^{0}\Post_j^1}}\\
s=s^1_0 \wedge s^1_{n+1}=s_0^2 \wedge s_1^2 = s^3_0 \wedge s^3_{m+1}=s'\\
\displaystyle{
\set{\gamma}=\mybigdotcup_{i=0}^n \vis{\set{\beta^1_i}\subst{\bigotimes_{j=i-1}^{0} \Post_j^1 } }  \dotcup  \vis{\set{\beta^2}\subst{\bigotimes_{j=n}^{0}\Post_j^1}} \dotcup \mybigdotcup_{i=0}^m \vis{\set{\beta^3_i} \subst{\bigotimes_{j=i-1}^{0}\Post_j^3\shortotimes\Post^2\shortotimes\bigotimes_{j=n}^{0}\Post^1_j} }}
\\
\Pred=\bigwedge_{i=0}^n\Pred^1_i\subst{\bigotimes_{j=i-1}^{0}\Post_j^1}\land\Pred^2 \subst{\bigotimes_{j=n}^{0}\Post_j^1}\land\\ 
~\qquad\quad\Big(\bigwedge_{i=0}^m\Pred_i^3\subst{\bigotimes_{j=i-1}^{0}\Post_j^3\shortotimes\Post^2\shortotimes\bigotimes_{j=n}^{0}\Post^1_j}\Big)\\
\Post=\bigotimes_{j=m}^{0}\Post_j^3\shortotimes\Post^2\shortotimes\bigotimes_{j=n}^{0}\Post^1_j
$

@@

\begin{proof} ($\Rightarrow$) We proceed by induction on  $l=n+m+1$, which is in fact the number of transitions with which we  build  a weak transition (introduced in Definition \ref{def:buildweakOT}).
\begin{itemize}
\item The base case $l=1$, so $n=0$ and $m=0$, we have:
\begin{mathpar}
 % \mprset {vskip=.5ex}
%\inferrule{
 \openrule
         {
           \set{\beta},\Pred,\Post}
         {s \OTarrow {\alpha} s'} \in \mathcal{T}
%}
%}
\end{mathpar} 
by rule (\WTDeux) we can directly conclude the implication: 
 \begin{mathpar}
 % \mprset {vskip=.5ex}
%\inferrule{
% \openrule
%         {
%           \set{\beta},\Pred,\Post}
%         {s \OTarrow {\alpha} s'} \in \mathcal{T}
%}

\openrule
         {
           \set{\beta},\Pred,\Post}
         {s \OTarrow {\alpha} s'} \in \mathcal{T} \implies 
{ \openrule
         {
           \vis{\set{\beta}}\!,\Pred,\Post
				 } {s \OTWeakarrow {\alpha} s'} \in \WT
}
\end{mathpar} 
\item For the inductive step, first we have by induction hypothesis that the formula holds for some length $l$.   Induction step is to infer that formula holds for transitions of length $l + 1$. As the condition holds for $l$, it means that there is $n$  $m$, $n'$,$m'$ such that $l=n+m+1$, and $l+1=n'+m'+1$ and either $n'=n+1$ or $m'=m+1$ (exclusively). \LUDO{je trouve toujours ca pas tres correct le coup $l=n+m+1$ donc $l'=(n+1)+m+1$ ou $l'=n+(m+1)+1$ mais bon comme on dirait que ma proposition plait pas, on verra a la review}
We consider the case $n'=n+1$, and $m'=m+1$ are similar. Side conditions are omitted for readability. We first focus on the left part of the disjunction. Let us consider the sequence of ($n+m+1$) open transitions:
\begin{mathpar}
\Big(\forall i \in [0..n].\openrule
    {
       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T} \quad \wedge
\quad
\openrule
         {
           \set{\beta^2},\Pred^2,\Post^2 }
         {s_0^2 \OTarrow {\alpha} s_1^2} \in \mathcal{T}
\quad \wedge\\
~~\qquad\qquad\forall i \in [0..m].\openrule
         {
           \set{\beta^3_i},\Pred^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
\Big) 
\end{mathpar}

By recurrence hypothesis we suppose that the statement holds for some  set of open transitions of length $l$. In particular, we have:\\

$
%\mprset {vskip=.5ex}
%\inferrule 
\Big(\forall i \in [0..n].\openrule
    {
       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T} \,\wedge\,
\openrule
         {
           \set{\beta^2},\Pred^2,\Post^2 }
         {s_0^2 \OTarrow {\alpha} s_1^2} \in \mathcal{T}
\, \wedge\\
~~\hspace{5.25cm}\forall i \in [0..m].\openrule
         {
           \set{\beta^3_i},\Pred^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}}\! \in\! \mathcal{T}
\Big) \\       
          \bigvee \Big(\alpha = \tau \wedge  \set{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'\Big)\!  \implies\!  {
\openrule
         {
           \set{\gamma},
		\Pred, \Post
				 } {s' \OTWeakarrow {\alpha'} s''} \in\WT
}
$

We need to prove that   by adding the following open transition the implication remains true:
\begin{mathpar}
 % \mprset {vskip=.5ex}
%\inferrule{
 \openrule
         {
           \set{\beta},\Pred\,',\Post\,'}
         {s \OTarrow {\tau} s'} \in \mathcal{T}
%}
\end{mathpar}
First by using rule (\WTDeux) we have:
\begin{mathpar}

 \openrule
         {
           \set{\beta},\Pred\,',\Post\,'}
         {s \OTarrow {\tau} s'} \in \mathcal{T}
\implies 
{ \openrule
         {
           \vis{\set{\beta}}\!,\Pred\,',\Post\,'
				 } {s \OTWeakarrow {\tau} s'} \in \WT
}
\end{mathpar}

On the other hand, by rule (\WTUn) we can write the following weak open transition:
\begin{mathpar}
 \openrule
         {
          \emptyset,\True,\Id(s'')
				 } {s'' \OTWeakarrow {\tau} s''} \in \WT
\end{mathpar}

@@

\begin{mathpar}
  \mprset {vskip=.5ex}
\inferrule {\openrule
         {
           \vis{\set{\beta}},\Pred\,',\Post\,'   }
         {s \OTWeakarrow {\tau} s'} \in \WT
\qquad
\openrule
         {
           \set{\gamma},
		\Pred, \Post
				 } {s' \OTWeakarrow {\alpha} s''} \in\WT
\qquad
\openrule
         {
          \emptyset,\True,\Id(s'')
				 } {s'' \OTWeakarrow {\tau} s''} \in \WT
\\
\set{\gamma''}= \vis{\set{\beta}} \dotcup \set{\gamma}\subst{\Post\,'}\quad
\Pred\,''=\Pred\,'\land\Pred\subst{\Post\,'}\\%\land (\Pred_3\subst{\Post_2})\subst{\Post_1}
\Post\,''=\Id(s'')\shortotimes\Post\shortotimes\Post\,' \quad \alpha''=\alpha'\subst{\Post\,'}
}
{
\openrule
         {
          \set{\gamma''}, \Pred\,'',\Post\,''
				 } 
         {s \OTWeakarrow {\alpha''} s''} \in\WT
} \WTTrois
\end{mathpar}

@@

\item Case rule (\WTTrois). We have:
\begin{mathpar}
  \mprset {vskip=.5ex}
\inferrule {\openrule
         {
           \set{\gamma_1},\Pred_1,\Post_1   }
         {s \OTWeakarrow {\tau} s'} \in \WT
\quad
\openrule
         {
           \set{\gamma_2},\Pred_2,\Post_2  }
         {s' \OTWeakarrow {\alpha} s''} \in \WT
\quad
\openrule
         {
           \set{\gamma_3},\Pred_3,({x_k\gets e_k})^{k\in K}    }
         {s'' \OTWeakarrow {\tau} s'''} \in\WT
\\
\Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land (\Pred_3\subst{\Post_2})\subst{\Post_1}
}
{
\openrule
         {
           \set{\gamma_1}\dotcup \set{\gamma_2}\dotcup\set{\gamma_3},
		\Pred,
				({x_k\gets (e_k\subst {\Post_2})\subst{\Post_1}})^{k\in K} } 
         {s \OTWeakarrow {\alpha} s'''} \in\WT
}
\end{mathpar}

@@

\item By induction hypothesis this means each tau weak open transition can be written as a series of $n_1$ tau open transitions such $n_1=n+m+1$, hence by simplification we have (strictly speaking, by induction we might also have the case $\alpha=\tau\land\set \gamma=\emptyset\land \ldots$ but in this case, (\WTUn)\ allows us to obtain a similar reduction with $n_1=1$): 
\begin{mathpar}
%\inferrule{
\openrule
         {
           \set{\gamma_1},\Pred_1,\Post_1   }
         {s \OTWeakarrow {\tau} s'} \in\! \WT 
\implies 
 \forall i \in [0..n_1].\openrule
    {
       \set{\beta_{1i}},\Pred_{1i},\Post_{1i}   }
         {s_{1i} \OTarrow {\tau} s_{1(i+1)}} \in \mathcal{T}
\end{mathpar}
where \\
$ 
s=s_{10} \wedge s_{1{(n_1+1)}}\!=s',
\displaystyle{\set{\gamma_1}=\mybigdotcup_{i=0}^{n_1} \vis{\set{\beta_{1i}}}}, 
\Pred_1\!=\!\bigwedge_{i=0}^{n_1}\Pred_{1i}, \Post_1= \bigotimes_{i=0}^{n_1} \subst{\Post_{1i}}\\
$
\TODO{$\Post_1= \biguplus_{i=0}^{n_1} \Post_{1i}$ or bigotimes?}
\item Similarly, a series of $m_1$ open transitions such that $m_1=n+m+1$   can be simplified as follows: 
\begin{mathpar}
%\inferrule{
\openrule
         {
           \set{\gamma_3},\Pred_3,\Post_3   }
         {s'' \OTWeakarrow {\tau} s'''} \in\! \WT
\implies 
\forall i \in [0..m_1].\openrule
    {
       \set{\beta_{3i}},\Pred_{3i},\Post_{3i}   }
         {s_{3i} \OTarrow {\tau} s_{3(i+1)}} \in \mathcal{T}        
\end{mathpar}
where\\
$
s''\!=\!s_{30} \wedge s_{3(m_1+1)}\!=\!s''',
\displaystyle{\set{\gamma_3}\!=\!\mybigdotcup_{i=0}^{m_1}\vis{\set{\beta_{3i}}}},
\Pred_3\!=\!\bigwedge_{i=0}^{m_1}\Pred_{3i},\Post_3\!=\!\bigotimes_{i=0}^{m_1} \subst{\Post_{3i}}\\
$

\item Concerning the middle reduction, by induction hypothesis there exist a set of open transitions in $\mathcal{T}$ such that:
\begin{mathpar}
\openrule
         {
           \set{\gamma_2},\Pred_2,\Post_2  }
         {s' \OTWeakarrow {\alpha} s''} \in\! \WT
\implies 
\bigg(\forall i \in [0..n_2].\openrule
    {
       \set{\beta_{2i}},\Pred_{2i},\Post_{2i}}
         {s_{2i} \OTarrow {\tau} s_{2(i+1)}} \in \mathcal{T}  \wedge

\openrule
         {
           \set{\beta'},\Pred\,',\Post\,' }
         {s_2 \OTarrow {\alpha} s_2'} \in \mathcal{T}
 \wedge
\forall i \in [0..m_2].\openrule
         {
           \set{\beta_{2i}'},\Pred_{2i}^{\,\prime},({x_k\gets e_k})^{k\in K}    }
         {s_{2i}' \OTarrow {\tau} s_{2(i+1)}'} \in \mathcal{T}
\bigg)         
\end{mathpar}
where\\
$
s'=s_{20} \wedge s_{2(n_2+1)}=s_2 \wedge s_2' = s_{20}' \wedge s_{2(m_2+1)}'=s''\\
\displaystyle{\set{\gamma_2}=\mybigdotcup_{i=0}^{n_2} \vis{\set{\beta_{2i}}} \dotcup  \vis{\set{\beta'}}  \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta_{2i}'}}}
\\
\Pred_2=\bigwedge_{i=0}^{n_2}\Pred_{2i}\land\Pred\,'\bigotimes_{i=0}^{n_2}\subst{\Post_{2i}}\land \big(\bigwedge_{i=0}^{m_2}\Pred_{2i}^{\,\prime}\subst{\Post\,'}\big)\bigotimes_{i=0}^{n_1}\subst{\Post_{2i}}
\\
\Post_2= \big({x_k\gets e_k\subst {\Post\,'}\bigotimes_{i=0}^{n_2}\subst{\Post_{2i}}}\big)^{k\in K}
$
\end{enumerate}
~~\\
Therefore, we can deduce that we have:
\begin{mathpar}
{ \openrule
         {
           \set{\gamma}\!,\Pred,\Post
				 } {s \OTWeakarrow {\alpha} s'} \in \WT
}
 \implies
\bigg(\forall i\in [0..(n_1\!+\!n_2)].\openrule
    {
       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in\mathcal{T} \wedge

>>>>

We use ${\displaystyle \bigotimes_{i=n}^{0} \Post_i}$ to denote  $\Post_n\otimes .. \otimes \Post_0$. By convention ${\displaystyle \bigotimes_{i=-1}^{0} \Post_i}$ is the identity. Note that for any term $t$ we have: $t\subst{\Post\shortotimes\Post'} = t\subst{\Post}\subst{\Post'}$

@@

\begin{lemma}
\label{lem-rel-OT-WOT} Let $A = <J,\mathcal{S}, s_0,
    \mathcal{T}>$ be open automata and $<J,\mathcal{S}, s_0,
    \WT>$ be the
weak open automata derived from $A$.  The two following statements are equivalent
%For any weak open transition $\symb{WOT} \in \WT$, there exists an open transitions $\symb{OT} \in \mathcal{T}$ such that:\\
\begin{enumerate}
\item Either $   
\alpha = \tau \wedge  \set{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'$; or \\ 
there exist   $\set{\beta^1}_i$, $\set{\beta^2_i}$, and $\set{\beta^3_i}$, $\Pred^1_i$, $\Pred^3_i$, $\Post^1_i$, and  $\Pred^2$, $\Post^2$ s.t.:
\begin{mathpar}
%\mprset {vskip=.5ex}
%\inferrule 
\forall i \in [0..n].\openrule
    {
       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T} \quad \wedge
\quad
\openrule
         {
           \set{\beta^2},\Pred^2,\Post^2 }
         {s_0^2 \OTarrow {\alpha} s_1^2} \in \mathcal{T}
\quad \wedge\\
\forall i \in [0..m].\openrule
         {
           \set{\beta^3_i},\Pred^3_i,\Post_i^3    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
 \end{mathpar}
\item  there exist $\set{\gamma}$, $\Pred$, $\Post$ s.t.
 \begin{mathpar}
%   \Longleftrightarrow  {
\openrule
         {
           \set{\gamma},
		\Pred, \Post
				 } {s \OTWeakarrow {\alpha'} s'} \in\WT
%}
\end{mathpar}
where\\
$
\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=n}^{0}\Post_j^1}}\\
s=s^1_0 \wedge s^1_{n+1}=s_0^2 \wedge s_1^2 = s^3_0 \wedge s^3_{m+1}=s'\\
\displaystyle{
\set{\gamma}=\mybigdotcup_{i=0}^n \vis{\set{\beta^1_i}\subst{\bigotimes_{j=i-1}^{0} \Post_j^1 } }  \dotcup  \vis{\set{\beta^2}\subst{\bigotimes_{j=n}^{0}\Post_j^1}} \dotcup \mybigdotcup_{i=0}^m \vis{\set{\beta^3_i} \subst{\bigotimes_{j=i-1}^{0}\Post_j^3\shortotimes\Post^2\shortotimes\bigotimes_{j=n}^{0}\Post^1_j} }}
\\
\Pred=\bigwedge_{i=0}^n\Pred^1_i\subst{\bigotimes_{j=i-1}^{0}\Post_j^1}\land\Pred^2 \subst{\bigotimes_{j=n}^{0}\Post_j^1}\land\\ 
~\qquad\quad\Big(\bigwedge_{i=0}^m\Pred_i^3\subst{\bigotimes_{j=i-1}^{0}\Post_j^3\shortotimes\Post^2\shortotimes\bigotimes_{j=n}^{0}\Post^1_j}\Big)\\
\Post=\bigotimes_{j=m}^{0}\Post_j^3\shortotimes\Post^2\shortotimes\bigotimes_{j=n}^{0}\Post^1_j
$

@@

\begin{proof} ($\Rightarrow$) We proceed by induction on  $n$ and $m$ (where between each step either $m$ or $n$ increases).
\begin{itemize}
\item The base case there is one transition, so $n=0$ and $m=0$, we have:
\begin{mathpar}
 % \mprset {vskip=.5ex}
%\inferrule{
 \openrule
         {
           \set{\beta},\Pred,\Post}
         {s \OTarrow {\alpha} s'} \in \mathcal{T}
%}
%}
\end{mathpar} 
by rule (\WTDeux) we can directly conclude the implication: 
 \begin{mathpar}
 % \mprset {vskip=.5ex}
%\inferrule{
% \openrule
%         {
%           \set{\beta},\Pred,\Post}
%         {s \OTarrow {\alpha} s'} \in \mathcal{T}
%}

\openrule
         {
           \set{\beta},\Pred,\Post}
         {s \OTarrow {\alpha} s'} \in \mathcal{T} \implies 
{ \openrule
         {
           \vis{\set{\beta}}\!,\Pred,\Post
				 } {s \OTWeakarrow {\alpha} s'} \in \WT
}
\end{mathpar} 
\item For the inductive step, first we have by induction hypothesis that the formula holds for some lengths $m$ and $n$. Induction step is to infer that formula holds for transitions of length $m+1$ or $n+1$. 
We consider the case $n'=n+1$ (because $m'=m+1$ is similar).  We first focus on the left part of the disjunction. Let us consider the sequence of ($n+m+1$) open transitions:
\begin{mathpar}
\Big(\forall i \in [0..n+1].\openrule
    {
       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T} \quad \wedge
\quad
\openrule
         {
           \set{\beta^2},\Pred^2,\Post^2 }
         {s_0^2 \OTarrow {\alpha} s_1^2} \in \mathcal{T}
\quad \wedge\\
~~\qquad\qquad\forall i \in [0..m].\openrule
         {
           \set{\beta^3_i},\Pred^3_i,\Post_{i 3}   }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
\Big) 
\end{mathpar}

By recurrence hypothesis we suppose that the statement holds for $n$ and $m$ (we remove the first tau transition). We have:\\

$
%\mprset {vskip=.5ex}
%\inferrule 
\Big(\forall i \in [1..n+1].\openrule
    {
       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T} \,\wedge\,
\openrule
         {
           \set{\beta^2},\Pred^2,\Post^2 }
         {s_0^2 \OTarrow {\alpha} s_1^2} \in \mathcal{T}
\, \wedge\\
~~\hspace{5.25cm}\forall i \in [0..m].\openrule
         {
           \set{\beta^3_i},\Pred^3_i,\Post_{i 3}   }
         {s^3_i \OTarrow {\tau} s^3_{i+1}}\! \in\! \mathcal{T}
\Big) \\       
          \bigvee \Big(\alpha = \tau \wedge  \set{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'\Big)\!  \implies\!  {
\openrule
         {
           \set{\gamma},
		\Pred, \Post
				 } {s'' \OTWeakarrow {\alpha'} s'} \in\WT
}
$
where\\
$
\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=n+1}^{1}\Post_j^1}}\\
s''=s^1_0 \wedge s^1_{n+2}=s_0^2 \wedge s_1^2 = s^3_0 \wedge s^3_{m+1}=s'\\
\displaystyle{
\set{\gamma}=\mybigdotcup_{i=1}^{n+1} \vis{\set{\beta^1_i}\subst{\bigotimes_{j=i-1}^{1} \Post_j^1 } }  \dotcup  \vis{\set{\beta^2}\subst{\bigotimes_{j=n+1}^{1}\Post_j^1}} \dotcup \mybigdotcup_{i=0}^m \vis{\set{\beta^3_i} \subst{\bigotimes_{j=i-1}^{0}\Post_j^3\shortotimes\Post^2\shortotimes\bigotimes_{j=n}^{0}\Post^1_j} }}
\\
\Pred=\bigwedge_{i=1}^{n+1}\Pred^1_i\subst{\bigotimes_{j=i-1}^{1}\Post_j^1}\land\Pred^2 \subst{\bigotimes_{j={n+1}}^{1}\Post_j^1}\land\\ 
~\qquad\quad\Big(\bigwedge_{i=0}^m\Pred_i^3\subst{\bigotimes_{j=i-1}^{0}\Post_j^3\shortotimes\Post^2\shortotimes\bigotimes_{j={n+1}}^{1}\Post^1_j}\Big)\\
\Post=\bigotimes_{j=m}^{0}\Post_j^3\shortotimes\Post^2\shortotimes\bigotimes_{j={n+1}}^{1}\Post^1_j
$

We need to prove that   by adding the following open transition the implication remains true:
\begin{mathpar}
 % \mprset {vskip=.5ex}
%\inferrule{
 \openrule
         {
           \set{\beta_{0}^{1}},\Pred_0^1,\Post_0^1}
         {s_0^1 \OTarrow {\tau} s_1^1} \in \mathcal{T}%}
\end{mathpar}
First by using rule (\WTDeux) we have:
\begin{mathpar}

 \openrule
         {
           \set{\beta_{0}^{1}},\Pred_0^1,\Post_0^1}
         {s_0^1 \OTarrow {\tau} s_1^1} \in \mathcal{T}
\implies 
{ \openrule
       {
           \vis{\set{\beta_{0}^{1}}}\!,\Pred_0^1,\Post_0^1
				 } {s_0^1 \OTWeakarrow {\tau}s_1^1} \in \WT
}
\end{mathpar}

On the other hand, by rule (\WTUn) we can write the following weak open transition:
\begin{mathpar}
 \openrule
         {
          \emptyset,\True,\Id(s')
				 } {s' \OTWeakarrow {\tau} s'} \in \WT
\end{mathpar}

@@

\begin{mathpar}
  \mprset {vskip=.5ex}
\inferrule {\openrule
       {
           \vis{\set{\beta_{0}^{1}}}\!,\Pred_0^1,\Post_0^1
				 } {s_0^1 \OTWeakarrow {\tau}s_1^1} \in \WT
\qquad
\openrule
         {
           \set{\gamma},
		\Pred, \Post
				 } {s'' \OTWeakarrow {\alpha} s'} \in\WT
\qquad
\openrule
         {
          \emptyset,\True,\Id(s'')
				 } {s' \OTWeakarrow {\tau} s'} \in \WT
\\
\set{\gamma''}= \vis{\set{\beta_{0}^{1}}} \dotcup \set{\gamma}\subst{\Post_0^1}\quad
\Pred\,''=\Pred_0^1\land\Pred\subst{\Post_0^1}\\%\land (\Pred_3\subst{\Post_2})\subst{\Post_0^1}
\Post\,''=\Id(s'')\shortotimes\Post\shortotimes\Post_0^1 \quad \alpha''=\alpha'\subst{\Post_0^1}
}
{
\openrule
         {
          \set{\gamma''}, \Pred\,'',\Post\,''
				 } 
         {s_0^1 \OTWeakarrow {\alpha''} s'} \in\WT
} \WTTrois
\end{mathpar}
where we obtain the conclusion of the lemma, as required with the following assertions (derived from previous assertions):\\
$
\alpha''=\alpha\displaystyle{\subst{\bigotimes_{j=n+1}^{1}\Post_j^1}}\subst{\Post_0^1} = \alpha\displaystyle{\subst{\bigotimes_{j=n+1}^{0}\Post_j^1}}\\
s^1_0=s^1_0 \wedge s^1_{n+2}=s_0^2 \wedge s_1^2 = s^3_0 \wedge s^3_{m+1}=s'\\
\displaystyle{
\set{\gamma''}=\mybigdotcup_{i=0}^{n+1} \vis{\set{\beta^1_i}\subst{\bigotimes_{j=i-1}^{1} \Post_j^1 } }  \dotcup  \vis{\set{\beta^2}\subst{\bigotimes_{j=n+1}^{1}\Post_j^1}} \dotcup \mybigdotcup_{i=0}^m \vis{\set{\beta^3_i} \subst{\bigotimes_{j=i-1}^{0}\Post_j^3\shortotimes\Post^2\shortotimes\bigotimes_{j=n}^{0}\Post^1_j} }}
\\
\Pred=\bigwedge_{i=0}^{n+1}\Pred^1_i\subst{\bigotimes_{j=i-1}^{0}\Post_j^1}\land\Pred^2 \subst{\bigotimes_{j={n+1}}^{0}\Post_j^1}\land\\ 
~\qquad\quad\Big(\bigwedge_{i=0}^m\Pred_i^3\subst{\bigotimes_{j=i-1}^{0}\Post_j^3\shortotimes\Post^2\shortotimes\bigotimes_{j={n+1}}^{0}\Post^1_j}\Big)\\
\Post=\bigotimes_{j=m}^{0}\Post_j^3\shortotimes\Post^2\shortotimes\bigotimes_{j={n+1}}^{0}\Post^1_j
$

@@

\item Case rule (\WTTrois). We have:
\begin{mathpar}
  \mprset {vskip=.5ex}
\inferrule {\openrule
         {
           \set{\gamma_1},\Pred_1,\Post_1   }
         {s \OTWeakarrow {\tau} s'} \in \WT
\quad
\openrule
         {
           \set{\gamma_2},\Pred_2,\Post_2  }
         {s' \OTWeakarrow {\alpha} s''} \in \WT
\quad
\openrule
         {
           \set{\gamma_3},\Pred_3,\Post_3    }
         {s'' \OTWeakarrow {\tau} s'''} \in\WT
\\
\Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land \Pred_3\subst{\Post_2\shortotimes\Post_1}
\\
\set{\gamma}=\set{\gamma_1}\dotcup \set{\gamma_2}\subst{\Post_1}\dotcup\set{\gamma_3}\subst{\Post_2\shortotimes \Post_1}\\
\alpha'=\alpha\subst{\Post_1}
}
{
\openrule
         {
           \set{\gamma},
		\Pred,
				\Post_3\shortotimes{\Post_2}\shortotimes{\Post_1} }
         {s \OTWeakarrow {\alpha'} s'''} \in\WT
}
\end{mathpar}

@@

\item By induction hypothesis this means each tau weak open transition can be written as a series of $n_1$ tau open transitions such $n_1=n+m+1$, hence by simplification we have (strictly speaking, by induction we might also have the case $\alpha=\tau\land\set \gamma=\emptyset\land \ldots$ but in this case, (\WTUn)\ allows us to obtain a similar reduction with $n_1=1$): 
\begin{mathpar}
%\inferrule{
\openrule
         {
           \set{\gamma_1},\Pred_1,\Post_1   }
         {s \OTWeakarrow {\tau} s'} \in\! \WT 
\implies 
 \forall i \in [0..n_1].\openrule
    {
       \set{\beta_{1i}},\Pred_{1i},\Post_{1i}   }
         {s_{1i} \OTarrow {\tau} s_{1(i+1)}} \in \mathcal{T}
\end{mathpar}
where \\
$ 
s=s_{10} \wedge s_{1{(n_1+1)}}\!=s',
\displaystyle{\set{\gamma_1}= \mybigdotcup_{i=0}^{n_1} \vis{\set{\beta_{1 i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{1 j} } }} \\
\Pred_1\!=\!\bigwedge_{i=0}^{n_1}(\Pred_{1i} \subst{\bigotimes_{j=i-1}^{0}\Post_{i j}} ), \Post_1= \bigotimes_{i=0}^{n_1} \subst{\Post_{1i}} 
$

\item Similarly, a series of $m_1$ open transitions such that $m_1=n+m+1$   can be simplified as follows: 
\begin{mathpar}
%\inferrule{
\openrule
         {
           \set{\gamma_3},\Pred_3,\Post_3   }
         {s'' \OTWeakarrow {\tau} s'''} \in\! \WT
\implies 
\forall i \in [0..m_1].\openrule
    {
       \set{\beta_{3i}},\Pred_{3i},\Post_{3i}   }
         {s_{3i} \OTarrow {\tau} s_{3(i+1)}} \in \mathcal{T}        
\end{mathpar}
where\\
$ 
s''=s_{30} \wedge s_{3{(m_1+1)}}\!=s''',
\displaystyle{\set{\gamma_3}= \mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{3 i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{3 j} } }} \\
\Pred_3\!=\!\bigwedge_{i=0}^{m_1}(\Pred_{3i} \subst{\bigotimes_{j=i-1}^{0}\Post_{3 j}} ), \Post_1= \bigotimes_{i=0}^{m_1} \subst{\Post_{3i}} 
$

\item Concerning the middle reduction, by induction hypothesis there exist a set of open transitions in $\mathcal{T}$ such that:
\begin{mathpar}
\openrule
         {
           \set{\gamma_2},\Pred_2,\Post_2  }
         {s' \OTWeakarrow {\alpha'} s''} \in\! \WT
\implies 
\bigg(\forall i \in [0..n_2].\openrule
    {
       \set{\beta_{2i}},\Pred_{2i},\Post_{2i}}
         {s_{2i} \OTarrow {\tau} s_{2(i+1)}} \in \mathcal{T}  \wedge

\openrule
         {
           \set{\beta'},\Pred\,',\Post\,' }
         {s_2 \OTarrow {\alpha''} s_2'} \in \mathcal{T}
 \wedge
\forall i \in [0..m_2].\openrule
         {
           \set{\beta_{2i}'},\Pred_{2i}^{\,\prime},\Post'_{2i}    }
         {s_{2i}' \OTarrow {\tau} s_{2(i+1)}'} \in \mathcal{T}
\bigg)         
\end{mathpar}
where\\
$
\alpha''=\alpha'\displaystyle{\subst{\bigotimes_{j=n_2}^{0}\Post_{2j}}}\\
s'=s_{20} \wedge s_{2(n_2+1)}=s_2 \wedge  s_2' = s_{20}' \wedge s_{2(m_2+1)}'=s''\\
\displaystyle{
\set{\gamma_2}=\mybigdotcup_{i=0}^{n_2} \vis{\set{\beta_{2i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{2 j} } }  \dotcup  \vis{\set{\beta'}\subst{\bigotimes_{j=n}^{0}\Post_j^1}} }\\~\qquad
\dotcup \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta'_{2i}} \subst{\bigotimes_{j=i-1}^{0}\Post'_{2j}\shortotimes\Post'\shortotimes\bigotimes_{j=n}^{0}\Post_{2j}} }
\\
\Pred_2=\bigwedge_{i=0}^{n_2}\Pred_{2i}\subst{\bigotimes_{j=i-1}^{0}\Post_{2j}}\land\Pred' \subst{\bigotimes_{j={n_2}}^{0}\Post_{2j}}\land\\ 
~\qquad\quad\Big(\bigwedge_{i=0}^{m_2}\Pred_i^3\subst{\bigotimes_{j=i-1}^{0}\Post'_{2j}\shortotimes\Post'\shortotimes\bigotimes_{j={n_2}}^{0}\Post_{2j}}\Big)\\
\Post_2=\bigotimes_{j=m_2}^{0}\Post'_{2j}\shortotimes\Post'\shortotimes\bigotimes_{j={n_2}}^{0}\Post_{2j}
$
